---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# varsExtra

The goal of varsExtra is to ...

## Installation

You can install the development version of varsExtra with:

``` r
install.packages("devtools")
devtools::install_github("DavZim/varsExtra")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(varsExtra)
library(vars)
library(ggplot2)
# set a theme for all plots
theme_set(theme_light())

# load some example data and perform a VAR
data(Canada)

# calculate the VAR
varres <- VAR(Canada, lag = 2, type = "none")

# calculate an Impulse Resonse Function
irfres <- irf(varres)
```

# Flatten the Results into a table
```{r flatten}
flatten_var(varres)
```

`varsExtra` allows you to export the results in table as well as plot format.
An easy export would look like this:

```{r ex1, eval=F}
plot1 <- ggfy(varres)
ggsave("myplot.pdf", plot1)

table1 <- tabulize(varres, format = "latex")
writeLines(table1, "mytable.tex")
```



# Tables
```{r tab1}
var_table <- tabulize(varres, format = "latex")
print(var_table)
```



# Plots
## Plot a VAR result
```{r fig1, fig.height=5}
ggfy(varres)
```

## Plot an Impules-Response Function
```{r irf, fig.width=7, fig.height=7}
ggfy(irfres)
```

# Additionals

Many functions have additional functionality, see the help-files for more information.

If you want need more functionality, or find a bug, you are more than welcome to open an issue or open a pull request.
